Meeting the Challenges of Modeling Astrophysical Thermonuclear Explosions: \castro, \maestro, and the \amrex\ Astrophysics Suite

### 2017-09-14 astronum_2017/astronum-amrex.tex
a few updates

Figure~\ref{fig:current-runs} shows some of our most recent science simulations.

>>>>

Figure~\ref{fig:current-runs} shows some of our most recent science
simulations.  The left panel is an image of convection in the helium
layer on a sub-Chandra white dwarf.  This is part of a study of the
early stages of the double detonation SNe Ia model.  Using \maestro,
we are able to model the convection in the He layer for many turnover
times and saw a range of outcomes depending on the mass of the white
dwarf and He layer, including a global He-nova-like behavior where the
entire layer runsway together and localized
burning~\cite{subchandra2}.

The middle figure shows convection in a H/He layer on a neutron star,
as a model of the early burning in an XRB.  This \maestro\ model was
the first 3D model of convection for this problem~\cite{xrb3}.

The rightmost image is the coalesced remains of the merger of a
0.9~$M_\odot$ and 0.6~$M_\odot$ WD.
